Hillary Clinton Emails

### 2016-04-10 presentation/presentation.tex
add multinomial regression title

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{subfigure}

@@

@@

\begin{frame}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{subfigure}
\usepackage{tikz}
\usetikzlibrary{bayesnet}

@@

\begin{frame}{Latent Dirichlet Allocation}

\begin{figure}
\centering
\begin{tikzpicture}
\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100]
  \node[main, fill = white!100] (alpha) [label=below:$\alpha$] { };
  \node[main] (theta) [right=of alpha,label=below:$\theta$] { };
  \node[main] (z) [right=of theta,label=below:z] {};
  \node[main] (beta) [above=of z,label=below:$\beta$] { };
  \node[main, fill = black!10] (w) [right=of z,label=below:w] { };
  \path (alpha) edge [connect] (theta)
        (theta) edge [connect] (z)
        (z) edge [connect] (w)
        (beta) edge [connect] (w);
  \node[rectangle, inner sep=0mm, fit= (z) (w),label=below right:N, xshift=13mm] {};
  \node[rectangle, inner sep=4.4mm,draw=black!100, fit= (z) (w)] {};
  \node[rectangle, inner sep=4.6mm, fit= (z) (w),label=below right:M, xshift=12.5mm] {};
  \node[rectangle, inner sep=9mm, draw=black!100, fit = (theta) (z) (w)] {};
\end{tikzpicture}
\end{figure}

\begin{frame}{Latent Dirichlet Allocation: Some Details}

\begin{itemize}
\item We use $K = 30$ topics for our resulting model.
\item What we ultimately care about are $\theta$ and $\beta$.
\item $\theta$ corresponds to how likely a topic is to appear in a document.
\item $\beta$ corresponds to how likely each word is to be associated with each topic.
\end{itemize}

\begin{frame}{Latent Dirichlet Allocation: Some Details}

\begin{itemize}
\item Some questions we want to answer with LDA
\begin{itemize}
\item Can we see sensible topics in the LDA output?
\item Who is associated most with each issue?
\item Do the topics proportions for each email line up with real world events?
\item Can we predict the source of a given email?
\end{itemize}
\end{itemize}

@@

\begin{frame}{Multinomial Logistic Regression}

\begin{itemize}
\item We next want to ask can we predict who said what?
\item To answer this question we employ multinomial regression.
\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try prediction for these.
\end{itemize}

\begin{frame}{Multinomial Logistic Regression Results}
